Topological Equivariant Artist Model

### 2022-01-18 slides/main.tex
fiber and equiv

\documentclass[xcolor={dvipsnames}, handout]{beamer}
%\documentclass[xcolor={dvipsnames}]{beamer}
\setbeamertemplate{footline}[frame number]
%\usepackage{amsmath,amsfonts,amssymb,pxfonts,eulervm,xspace}
\usepackage{amsmath, amsfonts, amssymb, mathtools, eulervm, xspace}
\renewcommand{\restriction}{\mathord{\upharpoonright}} %restriction w/p space
\usepackage{bm}
\usepackage{mathrsfs} % math script fonts
\usepackage{tikz}
\usetikzlibrary{cd} % commutative diagrams
\newtheorem{prop}{Proposition} %math?

@@

            \begin{aligned*}         

@@

        \end{aligned*}

@@

\begin{frame}{Functor $\textcolor{functor}{\bm{F}}: \textcolor{source}{\mathcal{C}} \rightarrow \textcolor{target}{\mathcal{D}}$}
\begin{columns}
    \column{.39\textwidth}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, ]
            \onslide*<1-|handout:1>{\textcolor{source}{c}} 
            \onslide*<1-|handout:1>{\arrow[d, "f"', shift right=0, color=source]} 
            \onslide*<3-|handout:1>{\arrow[r, "F", color=functor, maps to]} \& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d}}
            \onslide*<4-|handout:0>{\textcolor{target}{F(c)}} 
            \onslide*<0|handout:1>{\textcolor{target}{F(c)=d}} 
            \onslide*<2|handout:0>{\arrow[d, shift right=0, color=target]}
            \onslide*<3-|handout:0>{\arrow[d, "F(f)", shift right=0, color=target]}
            \onslide*<0|handout:1>{\arrow[d, "F(f)", shift right=3, color=target]} \\
            \onslide*<1-|handout:1>{\textcolor{source}{c^{\prime}}} 
            \onslide*<3-|handout:1>{\arrow[r, "F"', color=functor, maps to]}\& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d^{\prime}}}
            \onslide*<4-|handout:0>{\textcolor{target}{F(c^{\prime})}}
            \onslide*<0|handout:1>{\textcolor{target}{F(c^{\prime})= d^{\prime}}}                    
        \end{tikzcd}
    \end{equation*}
    \column{.59\textwidth}
    \begin{alertblock}<5-|handout:1>{composition}
        \begin{aligned*}
            \textcolor{functor}{F}(\textcolor{source}{g}) \circ  \textcolor{functor}{F}(\textcolor{source}{f}) = \textcolor{functor}{F} (\textcolor{source}{g}\circ \textcolor{source}{f})
        \end{aligned*}
    \end{alertblock}
    \begin{alertblock}<6-|handout:1>{identity}
        \begin{aligned*}
            \textcolor{functor}{F}(\textcolor{source}{id_c}) = \textcolor{target}{id}_{\textcolor{functor}{F}(\textcolor{source}{c})}
        \end{aligned*}
    \end{alertblock}
\end{columns}
\end{frame}

\begin{frame}{Presheaf: $\sheafc: \mathcal{C}^{op} \textcolor{sheaf}{\rightarrow} \setc $}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
        \onslide*<9-|handout:1->{\dfiberc}
        \onslide*<9-|handout:1->{\arrow[r, hook]} \& 
        \onslide*<1-|handout:1->{\dtotalc}
        \onslide*<1-|handout:1->{\arrow[d, "\pi"']} \\
           \& 
        \onslide*<1-|handout:1->{\dbasec}
        \onslide*<3-|handout:1->{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            \onslide*<3,6-|handout:0>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}} 
            \onslide*<4-5|handout:0>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}\in \setc}
            \onslide*<0|handout:1>{\setc \ni {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}}
            \&  
            {} \& 
            \onslide*<6-|handout:1>{{\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}}} 
            \onslide*<7-|handout:1>{\arrow[ll, "\iota^*"', hook', color=set]} \\\& \&\\
            \onslide*<3|handout:0>{\opensetc_1 \subset \dbasec}
            \onslide*<4-5|handout:0>{\opensetc_1 \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}})}
            \onslide*<6-|handout:0>{\opensetc_1}
            \onslide*<0|handout:1>{Ob(\mathcal{\dbasec}^{\textcolor{base}{op}}) \ni \opensetc_1} 
            \onslide*<5-|handout:0>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}", maps to, color=sheaf]}
            \onslide*<0|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}", maps to, color=sheaf, shift right = 10]}
            \onslide*<7-|handout:1>{\arrow[rr, "\iota"', hook, color=base]} \&   
            \onslide*<8-|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}" description, maps to, color=sheaf]} \& 
            \onslide*<6-|handout:1>{\opensetc_2} 
            \onslide*<6-|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}"', maps to, color=sheaf]}                   
            \end{tikzcd}
    \end{columns}
    \begin{center}
        \begin{alertblock}<8-|handout:1>{stalk}
            \begin{aligned*}
                \sheafc_{\dbasec, \dtotalc}\restriction_{\dbasepointc}\coloneqq \lim\limits_{\opensetc\ni \dbasepointc} \Gamma(\opensetc, \dtotalc\restriction_{\opensetc}) \\
                 \dfiberc_{\dbasepointc} \subset  \sheafc_{\dbasec, \dtotalc}\restriction_{\dbasepointc}
            \end{aligned*}
        \end{alertblock}

        \begin{alertblock}<9-|handout:1>{germ}
            %germ  is tau at limit, \tau(k) \in germ
            \begin{aligned*}
                \dsectionc(\dbasepointc) \in \sheafc_{\dbasec, \dtotalc}\restriction_{\dbasepointc}
            \end{aligned*}
        \end{alertblock}
    \end{center}
\end{frame}

@@

    \frametitle<3|handout:3>{Functor: \vindexc: \mathcal{\gbasec} \rightarrow \mathcal{\dbasec}}

@@

\begin{frame}{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\mapsto} \textcolor{functor}{G}$}

    \adjustbox{scale=3, center}{
        \begin{tikzcd}[ampersand replacement=\&]
            \& {} \arrow[dd, "\alpha" , maps to, shorten=1.5em, color=nattran] \&             \\
          \textcolor{source}{\mathcal{C}} \arrow[rr, "F", bend left, color=functor, maps to] \arrow[rr, "G"', bend right, color=functor, maps to] \& \& \textcolor{target}{\mathcal{D}} \\
            \& {} \&            
          \end{tikzcd}}
\end{frame}

\begin{frame}{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\rightarrow} \textcolor{functor}{G}$}
    \begin{equation*}
        \begin{tikzcd}[column sep=huge, ampersand replacement = \&]
            \onslide*<2-|handout:1>{\textcolor{target}{F(c)}}
            \onslide*<2-|handout:1>{\arrow[dd, "F(f)"', color=target]}
            \onslide*<4-5|handout:1>{\arrow[rr, "\alpha_{c}", bend left, color=nattran, maps to]}  
            \onslide*<6|handout:0>{\arrow[rr, "\alpha_{c}", color=nattran, maps to]} \& 
            \onslide*<1-4|handout:1>{\textcolor{source}{c}} 
            \onslide*<1-4|handout:1>{\arrow[dd, "f" description, color=source]}
            \onslide*<3-4|handout:1>{\arrow[r, "G"', color=functor,maps to ]}
            \onslide*<2-4|handout:1>{\arrow[l, "F", color=functor, maps to]} \& 
            \onslide*<3-|handout:1>{\textcolor{target}{G(c)}} 
            \onslide*<3-|handout:1>{\arrow[dd, "G(f)", color=target, maps to]} \\
            {} 
            \onslide*<4|handout:1>{\arrow[rr, dotted, color=nattran, maps to]}
            \onslide*<5|handout:0>{\arrow[rr, color=nattran, maps to]} \& \& {}                      \\
            \onslide*<2-|handout:1>{\textcolor{target}{F(c^{\prime})}} 
            \onslide*<4-5|handout:1>{\arrow[rr, "\alpha_{c^{\prime}}"', bend right, color=nattran, maps to]} 
            \onslide*<4-5|handout:0>{\arrow[rr, "\alpha_{c^{\prime}}"', color=nattran, maps to]}\& 
            \onslide*<1-4|handout:1>{\textcolor{source}{c^{\prime}}}
            \onslide*<2-4|handout:1>{\arrow[l, "F"', color=functor, maps to]} 
            \onslide*<3-4|handout:1>{\arrow[r, "G", color=functor, maps to]} \& 
            \onslide*<3-|handout:1>{\textcolor{target}{G(c^{\prime})}}          
        \end{tikzcd}
    \end{equation*}    
\end{frame}

\begin{frame}
    \frametitle<1-2|handout:1>{Data Space: $\vartistc_{\vindexpushc}: \sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\mapsto} \vindexpushc\sheafc_{\gbasec, \gtotalc}$}
    \frametitle<3-4|handout:2>{Display Space: $\vartist_{\vindexpullc}: \vindexpullc\sheafc_{\dbasec, \dtotalc} \rightarrow \sheafc_{\gbasec, \gtotalc}$}
    \frametitle<5|handout:3->{\textcolor{artist}{Artist} \vartistc}

    \onslide*<1|handout:1>{
        \begin{equation*}
      \begin{tikzcd}[ampersand replacement =\&]
        \cgamma{\opensetc_1}{\dtotalc} 
        \arrow[dd, "\iota^*"', hook, color=set] 
        \arrow[rrrr, "\vartistc_{\opensetc_1}", bend left, color=artist, maps to] \&  \& 
        \opensetc_1 
        \arrow[ll, "\sheafc_{\dtotalc}", color=sheaf, maps to] 
        \arrow[rr, "\sheafc_{\gtotalpushc}"', color=sheaf, maps to] \&  \& 
        \cgamma{\opensetc_1}{\gtotalpushc} 
        \arrow[dd, "\iota^*", hook', color=set] \\
        {} 
        \arrow[rrrr, dotted, color=artist, maps to] \&\&\&\& {} \\
        \cgamma{\opensetc_2}{\dtotalc} 
        \arrow[rrrr, "\vartistc_{\opensetc_2}"', bend right, color=artist, maps to] \&  \& 
        \opensetc_2 
        \arrow[ll, "\sheafc_{\dtotalc}"', color=sheaf, maps to] 
        \arrow[rr, "\sheafc_{\gtotalpushc}", color=sheaf, maps to] 
        \arrow[uu, "\iota" description, hook, color=base] \& \& 
        \cgamma{\opensetc_2}{\gtotalpushc}               
    \end{tikzcd}
        \end{equation*}}

    \onslide*<0|handout:2>{
        \begin{equation*}
  \begin{tikzcd}[ampersand replacement =\&]
    \cgamma{\opensetgc_1}{\dtotalpullc} 
    \arrow[dd, "\iota^*"', hook, color=set] 
    \arrow[rrrr, "\vartistc_{\opensetgc_1}", bend left, color=artist, maps to] \&  \& 
    \opensetgc_1 
    \arrow[ll, "\sheafc_{\dtotalpullc}", color=sheaf, maps to] 
    \arrow[rr, "\sheafc_{\gtotalc}"', color=sheaf, maps to] \&  \& 
    \cgamma{\opensetgc_1}{\gtotalc} 
    \arrow[dd, "\iota^*", hook', color=set] \\
    {} 
    \arrow[rrrr, dotted, color=artist, maps to] \&\&\&\& {} \\
    \cgamma{\opensetgc_2}{\dtotalpullc} 
    \arrow[rrrr, "\vartistc_{\opensetgc_2}"', bend right, color=artist, maps to] \&  \& 
    \opensetgc_2 
    \arrow[ll, "\sheafc_{\dtotalpullc}"', color=sheaf, maps to] 
    \arrow[rr, "\sheafc_{\gtotalc}", color=sheaf, maps to] 
    \arrow[uu, "\iota" description, hook, color=base] \& \& 
    \cgamma{\opensetgc_2}{\gtotalc}   
\end{tikzcd}
    \end{equation*}}

    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
          \onslide*<0|handout:3>{\sheafc_{\gbasec, \gtotalc}} 
          \onslide*<0|handout:3>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]}  
          \& \& 
          \onslide*<0|handout:3>{\textcolor{functor}{\vindexpush}\sheafc_{\gbasec, \gtotalc}}
          \\
          \& \& \\
          \onslide*<0|handout:3>{\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}}
          \onslide*<0|handout:3>{\arrow[uu, "\vartistc_{\vindexpushc}", color=artist, maps to]}
          \&  \& 
          \onslide*<0|handout:3>{\sheafc_{\dbasec, \dtotalc}}
          \onslide*<0|handout:3>{\arrow[ll, "\textcolor{functor}{\vindexpull}", color=functor]} 
          \onslide*<0|handout:3>{\arrow[uu, "\vartistc_{\vindexpullc}"', color=artist, maps to]}
          \onslide*<4-|handout:3>{\arrow[lluu, "\vartistc"' description, dashed, color=artist, maps to]}
        \end{tikzcd}
      \end{equation*}

    \onslide<0|handout:3>{
        \begin{equation*}
        \textcolor{nattran}{Nat}_{\gbasec}(\textcolor{functor}{\vindexpull}\sheafc_{(\dbasec, \dtotalc)}, \sheafc_{(\gbasec, \gtotalc)}) = 
    \textcolor{nattran}{Nat}_{\dbase}(\sheafc_{(\dbasec, \dtotalc)}, \textcolor{functor}{\vindexpush}\sheafc_{(\gbasec, \gtotalc)})
        \end{equation*}
    }
\end{frame}

\section{Equivariant Artist}
\begin{frame}{"Valid" viz?}
    \begin{equation*}
        \label{eq:artist:artist_sheaf}
        \begin{tikzcd}[ampersand replacement = \&, column sep=tiny, row sep=huge]
            \onslide*<1-|handout:1>{\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}} 
            \&  \& 
            \onslide*<2-|handout:1>{\textcolor{set}{\big\{}\gsectionc:\opensetgc\rightarrow \gtotalc\restriction_{\opensetgc} 
              \bigm{\vert} \vartistc\circ (\dfuncc \circ \vartistc^{-1}[\gsectionc]) = \dfuncc^{\prime} \circ \gsectionc \textcolor{set}{\big\}}} 
            \onslide*<2-|handout:1>{\arrow[ll, "\textcolor{set}{\mathlarger{\mathlarger{\supset}}}" description, hook', color=white]} \\ 
            \&  \& \\
            \onslide*<1-|handout:1>{\opensetgc} 
            \onslide*<1-|handout:1>{\arrow[uu, "\sheafc_{\gtotalc}", color=sheaf]} 
            \onslide*<2-|handout:1>{\arrow[rruu, "\vartistc(\sheafc_{\dtotalc})\coloneqq \sheafc_{\vartistc}" description, dashed, color=sheaf]} 
            \&  \& 
        \end{tikzcd}
    \end{equation*}
\end{frame}

\begin{frame}{$\dfuncc = (\hat\dfuncc, \hat\dfuncc_*, \tilde\dfuncc)$?}
\begin{equation*}
    \begin{tikzcd}[ampersand replacement = \&, row sep=large]
        {\Gamma(U, E)} 
        \arrow[r, "\hat\varphi_*"]                             
        \& 
        {\Gamma(U^{\prime}, \hat{\varphi_*}E)} 
        \arrow[r, "\tilde{\varphi}"]                                                                                                             
        \& {\Gamma(U^{\prime}, \tilde{\varphi}\hat{\varphi_*}E)} \\
        {U \subset K} 
        \arrow[r, "\hat\varphi"] 
        \arrow[u, "{\mathcal{O}_{K,E}}"] 
        \& 
        {U^{\prime}\subset K^{\prime}}
        \arrow[u, "{\mathcal{O}_{K^{\prime}, \hat\varphi_*E}}", dashed] 
        \arrow[ru, "{\mathcal{O}_{\hat\varphi K, \tilde\varphi\hat\varphi_*E}}"', dotted] 
        \&                                                                                                          
    \end{tikzcd}                                   
\end{equation*}
\end{frame}

>>>>

\documentclass[xcolor={dvipsnames}, handout]{beamer}
%\documentclass[xcolor={dvipsnames}]{beamer}
\setbeamertemplate{footline}[frame number]
%\usepackage{amsmath,amsfonts,amssymb,pxfonts,eulervm,xspace}
\usepackage{amsmath, amsfonts, amssymb, mathtools, eulervm, xspace}
\renewcommand{\restriction}{\mathord{\upharpoonright}} %restriction w/p space
\usepackage{relsize}%mathlarger
\usepackage{bm}
\usepackage{centernot}
\usepackage{mathrsfs} % math script fonts
\usepackage{tikz}
\usetikzlibrary{cd} % commutative diagrams
\newtheorem{prop}{Proposition} %math?

@@

            \begin{align*}         

@@

        \end{align*}

@@

\begin{frame}{Functor $\textcolor{functor}{\bm{F}}: \textcolor{source}{\mathcal{C}} \rightarrow \textcolor{target}{\mathcal{D}}$}
\begin{columns}
    \column{.39\textwidth}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, ]
            \onslide*<1-|handout:1>{\textcolor{source}{c}} 
            \onslide*<1-|handout:1>{\arrow[d, "f"', shift right=0, color=source]} 
            \onslide*<3-|handout:1>{\arrow[r, "F", color=functor, maps to]} \& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d}}
            \onslide*<4-|handout:0>{\textcolor{target}{F(c)}} 
            \onslide*<0|handout:1>{\textcolor{target}{F(c)=d}} 
            \onslide*<2|handout:0>{\arrow[d, shift right=0, color=target]}
            \onslide*<3-|handout:0>{\arrow[d, "F(f)", shift right=0, color=target]}
            \onslide*<0|handout:1>{\arrow[d, "F(f)", shift right=3, color=target]} \\
            \onslide*<1-|handout:1>{\textcolor{source}{c^{\prime}}} 
            \onslide*<3-|handout:1>{\arrow[r, "F"', color=functor, maps to]}\& 
            \onslide*<2-3|handout:0>{\textcolor{target}{d^{\prime}}}
            \onslide*<4-|handout:0>{\textcolor{target}{F(c^{\prime})}}
            \onslide*<0|handout:1>{\textcolor{target}{F(c^{\prime})= d^{\prime}}}                    
        \end{tikzcd}
    \end{equation*}
    \column{.59\textwidth}
    \begin{alertblock}<5-|handout:1>{composition}
        \begin{align*}
            \textcolor{functor}{F}(\textcolor{source}{g}) \circ  \textcolor{functor}{F}(\textcolor{source}{f}) = \textcolor{functor}{F} (\textcolor{source}{g}\circ \textcolor{source}{f})
        \end{align*}
    \end{alertblock}
    \begin{alertblock}<6-|handout:1>{identity}
        \begin{align*}
            \textcolor{functor}{F}(\textcolor{source}{id_c}) = \textcolor{target}{id}_{\textcolor{functor}{F}(\textcolor{source}{c})}
        \end{align*}
    \end{alertblock}
\end{columns}
\end{frame}

\begin{frame}{Presheaf: $\sheafc: \mathcal{C}^{op} \textcolor{sheaf}{\rightarrow} \setc $}
    \begin{columns}
    \column{0.29\textwidth}
    \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
        \onslide*<9-|handout:1->{\dfiberc}
        \onslide*<9-|handout:1->{\arrow[r, hook]} \& 
        \onslide*<1-|handout:1->{\dtotalc}
        \onslide*<1-|handout:1->{\arrow[d, "\pi"']} \\
           \& 
        \onslide*<1-|handout:1->{\dbasec}
        \onslide*<3-|handout:1->{\arrow[u, "\dsectionc \in \cgamma{\dbasec}{\dtotalc}"', bend right, pos=.5]}
        \end{tikzcd}
    \column{0.69\textwidth}
        \begin{tikzcd}[ampersand replacement = \&, column sep=small]
            \onslide*<3,6-|handout:0>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}} 
            \onslide*<4-5|handout:0>{{\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}\in \setc}
            \onslide*<0|handout:1>{\setc \ni {\cgamma{\opensetc_1}{\dtotalc\restriction_{{\opensetc_1}}}}}
            \&  
            {} \& 
            \onslide*<6-|handout:1>{{\cgamma{\opensetc_2}{\dtotalc\restriction_{\opensetc_2}}}} 
            \onslide*<7-|handout:1>{\arrow[ll, "\iota^*"', hook', color=set]} \\\& \&\\
            \onslide*<3|handout:0>{\opensetc_1 \subset \dbasec}
            \onslide*<4-5|handout:0>{\opensetc_1 \in Ob(\mathcal{\dbasec}^{\textcolor{base}{op}})}
            \onslide*<6-|handout:0>{\opensetc_1}
            \onslide*<0|handout:1>{Ob(\mathcal{\dbasec}^{\textcolor{base}{op}}) \ni \opensetc_1} 
            \onslide*<5-|handout:0>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}", maps to, color=sheaf]}
            \onslide*<0|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}", maps to, color=sheaf, shift right = 10]}
            \onslide*<7-|handout:1>{\arrow[rr, "\iota"', hook, color=base]} \&   
            \onslide*<8-|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}" description, maps to, color=sheaf]} \& 
            \onslide*<6-|handout:1>{\opensetc_2} 
            \onslide*<6-|handout:1>{\arrow[uu, "\sheafc_{\dbasec, \dtotalc}"', maps to, color=sheaf]}                   
            \end{tikzcd}
    \end{columns}
    \begin{center}
        \begin{alertblock}<8-|handout:1>{stalk}
            \begin{align*}
                \sheafc_{\dbasec, \dtotalc}\restriction_{\dbasepointc}\coloneqq \lim\limits_{\opensetc\ni \dbasepointc} \Gamma(\opensetc, \dtotalc\restriction_{\opensetc}) \\
                 \dfiberc_{\dbasepointc} \subset  \sheafc_{\dbasec, \dtotalc}\restriction_{\dbasepointc}
            \end{align*}
        \end{alertblock}

        \begin{alertblock}<9-|handout:1>{germ}
            %germ  is tau at limit, \tau(k) \in germ
            \begin{align*}
                \dsectionc(\dbasepointc) \in \sheafc_{\dbasec, \dtotalc}\restriction_{\dbasepointc}
            \end{align*}
        \end{alertblock}
    \end{center}
\end{frame}

@@

    \frametitle<3|handout:3>{Functor: $\vindexc: \mathcal{\gbasec} \rightarrow \mathcal{\dbasec}$}

@@

\begin{frame}{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\Rightarrow} \textcolor{functor}{G}$}

    \adjustbox{scale=3, center}{
        \begin{tikzcd}[ampersand replacement=\&]
            \& {} \arrow[dd, "\alpha" , Rightarrow, shorten=1.5em, color=nattran] \&             \\
          \textcolor{source}{\mathcal{C}} \arrow[rr, "F", bend left, color=functor, maps to] \arrow[rr, "G"', bend right, color=functor, maps to] \& \& \textcolor{target}{\mathcal{D}} \\
            \& {} \&            
          \end{tikzcd}}
\end{frame}

\begin{frame}{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\Rightarrow} \textcolor{functor}{G}$}
    \begin{equation*}
        \begin{tikzcd}[column sep=huge, ampersand replacement = \&]
            \onslide*<2-|handout:1>{\textcolor{target}{F(c)}}
            \onslide*<2-|handout:1>{\arrow[dd, "F(f)"', color=target]}
            \onslide*<4-5|handout:1>{\arrow[rr, "\alpha_{c}", bend left, color=nattran, Rightarrow]}  
            \onslide*<6|handout:0>{\arrow[rr, "\alpha_{c}", color=nattran, Rightarrow]} \& 
            \onslide*<1-4|handout:1>{\textcolor{source}{c}} 
            \onslide*<1-4|handout:1>{\arrow[dd, "f" description, color=source]}
            \onslide*<3-4|handout:1>{\arrow[r, "G"', color=functor,maps to ]}
            \onslide*<2-4|handout:1>{\arrow[l, "F", color=functor, maps to]} \& 
            \onslide*<3-|handout:1>{\textcolor{target}{G(c)}} 
            \onslide*<3-|handout:1>{\arrow[dd, "G(f)", color=target, maps to]} \\
            {} 
            \onslide*<4|handout:1>{\arrow[rr, dotted, color=nattran, Rightarrow]}
            \onslide*<5|handout:0>{\arrow[rr, color=nattran, Rightarrow]} \& \& {}                      \\
            \onslide*<2-|handout:1>{\textcolor{target}{F(c^{\prime})}} 
            \onslide*<4-5|handout:1>{\arrow[rr, "\alpha_{c^{\prime}}"', bend right, color=nattran, Rightarrow]} 
            \onslide*<4-5|handout:0>{\arrow[rr, "\alpha_{c^{\prime}}"', color=nattran, maps to]}\& 
            \onslide*<1-4|handout:1>{\textcolor{source}{c^{\prime}}}
            \onslide*<2-4|handout:1>{\arrow[l, "F"', color=functor, maps to]} 
            \onslide*<3-4|handout:1>{\arrow[r, "G", color=functor, maps to]} \& 
            \onslide*<3-|handout:1>{\textcolor{target}{G(c^{\prime})}}          
        \end{tikzcd}
    \end{equation*}    
\end{frame}

\begin{frame}
    \frametitle<1-2|handout:1>{Data Space: $\vartistc_{\opensetc}: \sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\Rightarrow} \vindexpushc\sheafc_{\gbasec, \gtotalc}$}
    \frametitle<3-4|handout:2>{Display Space: $\vartist_{\opensetgc}: \vindexpullc\sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\Rightarrow} \sheafc_{\gbasec, \gtotalc}$}
    \frametitle<5|handout:3->{\textcolor{artist}{Artist} \vartistc}

    \onslide*<1|handout:1>{
        \begin{equation*}
      \begin{tikzcd}[ampersand replacement =\&]
        \cgamma{\opensetc_1}{\dtotalc} 
        \arrow[dd, "\iota^*"', hook, color=set] 
        \arrow[rrrr, "\vartistc_{\opensetc_1}", bend left, color=artist, Rightarrow] \&  \& 
        \opensetc_1 
        \arrow[ll, "\sheafc_{\dtotalc}", color=sheaf, maps to] 
        \arrow[rr, "\sheafc_{\gtotalpushc}"', color=sheaf, maps to] \&  \& 
        \cgamma{\opensetc_1}{\gtotalpushc} 
        \arrow[dd, "\iota^*", hook', color=set] \\
        {} 
        \arrow[rrrr, dotted, color=artist,Rightarrow] \&\&\&\& {} \\
        \cgamma{\opensetc_2}{\dtotalc} 
        \arrow[rrrr, "\vartistc_{\opensetc_2}"', bend right, color=artist, Rightarrow] \&  \& 
        \opensetc_2 
        \arrow[ll, "\sheafc_{\dtotalc}"', color=sheaf, maps to] 
        \arrow[rr, "\sheafc_{\gtotalpushc}", color=sheaf, maps to] 
        \arrow[uu, "\iota" description, hook, color=base] \& \& 
        \cgamma{\opensetc_2}{\gtotalpushc}               
    \end{tikzcd}
        \end{equation*}}

    \onslide*<0|handout:2>{
        \begin{equation*}
    \begin{tikzcd}[ampersand replacement =\&]
    \cgamma{\opensetgc_1}{\dtotalpullc} 
    \arrow[dd, "\iota^*"', hook, color=set] 
    \arrow[rrrr, "\vartistc_{\opensetgc_1}", bend left, color=artist, Rightarrow] \&  \& 
    \opensetgc_1 
    \arrow[ll, "\sheafc_{\dtotalpullc}", color=sheaf, maps to] 
    \arrow[rr, "\sheafc_{\gtotalc}"', color=sheaf, maps to] \&  \& 
    \cgamma{\opensetgc_1}{\gtotalc} 
    \arrow[dd, "\iota^*", hook', color=set] \\
    {} 
    \arrow[rrrr, dotted, color=artist, Rightarrow] \&\&\&\& {} \\
    \cgamma{\opensetgc_2}{\dtotalpullc} 
    \arrow[rrrr, "\vartistc_{\opensetgc_2}"', bend right, color=artist, Rightarrow] \&  \& 
    \opensetgc_2 
    \arrow[ll, "\sheafc_{\dtotalpullc}"', color=sheaf, maps to] 
    \arrow[rr, "\sheafc_{\gtotalc}", color=sheaf, maps to] 
    \arrow[uu, "\iota" description, hook, color=base] \& \& 
    \cgamma{\opensetgc_2}{\gtotalc}   
    \end{tikzcd}
    \end{equation*}}

    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
          \onslide*<0|handout:3->{\sheafc_{\gbasec, \gtotalc}} 
          \onslide*<0|handout:3->{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]}  
          \& \& 
          \onslide*<0|handout:3->{\textcolor{functor}{\vindexpush}\sheafc_{\gbasec, \gtotalc}}
          \\
          \& \& \\
          \onslide*<0|handout:3->{\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}}
          \onslide*<0|handout:3->{\arrow[uu, "\vartistc_{\opensetgc}", color=artist, Rightarrow]}
          \&  \& 
          \onslide*<0|handout:3->{\sheafc_{\dbasec, \dtotalc}}
          \onslide*<0|handout:3->{\arrow[ll, "\textcolor{functor}{\vindexpull}", color=functor]} 
          \onslide*<0|handout:3->{\arrow[uu, "\vartistc_{\opensetc}"', color=artist, Rightarrow]}
          \onslide*<4-|handout:3->{\arrow[lluu, "\vartistc"' description, dashed, color=artist, Rightarrow]}
        \end{tikzcd}
      \end{equation*}

    \onslide<0|handout:3>{
        \begin{equation*}
        \textcolor{nattran}{Nat}_{\opensetgc}(\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}, \sheafc_{\gbasec, \gtotalc}) = 
    \textcolor{nattran}{Nat}_{\opensetc}(\sheafc_{\dbasec, \dtotalc}, \textcolor{functor}{\vindexpush}\sheafc_{\gbasec, \gtotalc})
        \end{equation*}
    }
    \onslide<0|handout:4>{
        \begin{equation*}
            \sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\xrightarrow{\vartistc}} \sheafc_{\gbasec, \gtotalc}
        \end{equation*}
        \begin{equation*}
             (\sheafc_{\dbasec,\dtotalc} \textcolor{functor}{\xmapsto{\vindexpullc}} \vindexpullc \sheafc_{\dbasec,\dtotalc}) \textcolor{artist}{\xRightarrow{\vartistc_{\opensetgc}}} \sheafc_{\gbasec, \gtotalc} \tag{$\vartistc_{\opensetgc} \circ \vindexpullc = \vartistc$}
        \end{equation*}
        \begin{equation*}
            (\sheafc_{\dbasec,\dtotalc} \textcolor{artist}{\xRightarrow{\vartistc}} \sheafc_{\gbasec, \gtotalc}) \textcolor{functor}{\xmapsto{\vindexpushc}} \vindexpushc \sheafc_{\gbasec, \gtotalc} \tag{$\vindexpushc \circ \vartistc = \vartistc_{\opensetc}$}      
        \end{equation*}
        \begin{equation*}
            ((\sheafc_{\dbasec,\dtotalc} \textcolor{functor}{\xmapsto{\vindexpullc}} \vindexpullc \sheafc_{\dbasec,\dtotalc}) \textcolor{artist}{\xRightarrow{\vartistc_{\opensetgc}}} \sheafc_{\gbasec, \gtotalc})\textcolor{functor}{\xmapsto{\vindexpushc}} \vindexpushc \sheafc_{\gbasec, \gtotalc} \tag{$\vindexpushc \circ \vartistc_{\opensetgc} \circ \vindexpullc = \vartistc_{\opensetc}$}
        \end{equation*}
        }
\end{frame}

\section{Equivariant Artist}
\begin{frame}{"Valid" viz?}
    \begin{equation*}
        \label{eq:artist:artist_sheaf}
        \begin{tikzcd}[ampersand replacement = \&, column sep=tiny, row sep=huge]
            \onslide*<1-|handout:1>{\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}} 
            \&  \& 
            \onslide*<2-|handout:1>{\textcolor{set}{\big\{}\gsectionc:\opensetgc\rightarrow \gtotalc\restriction_{\opensetgc} 
              \bigm{\vert} \vartistc \circ \dfuncc_{\dsectionc} \circ \dsectionc = \dfuncc_{\gsectionc} \circ \gsectionc \textcolor{set}{\big\}}} 
            \onslide*<2-|handout:1>{\arrow[ll, "\textcolor{set}{\mathlarger{\mathlarger{\supset}}}" description, hook', color=white]} \\ 
            \&  \& \\
            \onslide*<1-|handout:1>{\opensetgc} 
            \onslide*<1-|handout:1>{\arrow[uu, "\sheafc_{\gtotalc}", color=sheaf, maps to]} 
            \onslide*<2-|handout:1>{\arrow[rruu, "\vartistc(\sheafc_{\dtotalc})\coloneqq \sheafc_{\vartistc}" description, dashed, color=sheaf, maps to]} 
            \&  \& 
        \end{tikzcd}
    \end{equation*}
\end{frame}
